---
title: "W7_Assignment"
author: "Ambra"
date: "March 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

than one author. For each book, include the title, authors, and two or three other attributes that you find interesting.
Take the information that you've selected about these three books, and separately create three files which store the book's information in HTML (using an html table), XML, and JSON formats (e.g. "books.html","books.xml", and "books.json").[...]

Write R code, using your packages of choice, to load the information from each of the three sources into separate R data frames. Are the three data frames identical?
```{r Books}
library(XML)
library(plyr)
library(RJSONIO)



##Reading XML file

docxml<- readLines("https://raw.githubusercontent.com/ambra1982/W7ReadingXMLJsonHTML/master/books.xml")

docxml <- xmlParse(docxml, asText = T)

docxmldf<- ldply(xmlToList(docxml), data.frame)

docxmldf



##Reading HTML File
dochtml<- readLines("https://raw.githubusercontent.com/ambra1982/W7ReadingXMLJsonHTML/master/index.html")

dochtml1<- readHTMLTable(dochtml)

dochtml1

##Reading Json File

library(jsonlite)


docjson1<- jsonlite::fromJSON("https://raw.githubusercontent.com/ambra1982/W7ReadingXMLJsonHTML/master/books.json", simplifyDataFrame=T)

docjson1


```

The main difference among the dfs lies in two additional columns generated by the XML file.